---
title: "Lab 01 - Hello R"
author: "Ben Hardin"
date: "1/13/2023"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

The datasaurus_dozen dataframe has 1846 rows and 3 columns, or variables.
These variables are:
1. dataset - which dataset the data are from
2. x - x-values
3. y - y-values

### Exercise 2

The purpose of this exercise is to visualize and describe the relationship between
variables x & y in the dino dataset.

The first part of code below filters out all the datasets in the datasaurus_dozen
data frame besides the dino dataset, so that we can plot that dataset specifically.

The second part of the code creates a scatterplot of values x & y using the ggplot
function. The arguments (1) select the filtered dataset we just made, (2) assigns the x
variable to the x axis and the y variable to the y axis, (3) chooses points as our
shape for representing each datapoint. The result is a beautiful dinosaur!

```{r plot-dino, fig.height=3, fig.width=4}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Finally, the code below calculates the correlation between x and y in the dino dataset
and makes a table showing the correlation coefficient (r = -.065). This correlation
sadly is misleading and does not capture the majesty of the dinosaur.

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Add code and narrative as needed.
Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient.
To finish, clean up the narrative by removing these instructions.



```{r plot-star}

```

I'm some filler text, you should replace me with more meaningful text...

```{r cor-star}

```

### Exercise 4

Add code and narrative as needed.
Note that two R chunks are given but they are not labeled.
Use the convention from above to name them appropriately.

```{r}

```

```{r}

```

### Exercise 5

Add code and narrative as needed.

To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.



## Bonus Tips by Yoo Ri

Here are some helpful tips :) 

* filter() is for extracting rows

* group_by() is for grouping datasets by assigned column 
* ungroup() cancels the grouping 

* summarize()  is often used with group_by(). This function can print the output according to the group_by().

* facet_grid(y~x,...) creates a grid with variable y as a row, variable x as a column  
* facet_wrap(x,... ) is useful when there is only one variable
